Structured Versus Decorated Cospans

### 2022-04-07 cospans_compositionality_3.tex
a few edits

\bibitem{BFP} J.\ C.\ Baez, B.\ Fong and B.\ S.\ Pollard, A compositional framework for Markov processes, \textsl{Jour. Math. Phys.} \textbf{57} (2016), 033301. 
\href{https://doi.org/10.1063/1.4941578}{https://doi.org/10.1063/1.4941578}.

\bibitem{BM}  J.\ C.\ Baez and J.\ Master, Open Petri nets, \textsl{Math.\ Struct.\ Comput.\ Sci.\ }\textbf{30} (2020), 314--341.  \href{https://doi.org/10.1017/s0960129520000043}{https://doi.org/10.1017/s0960129520000043}.
Also available at
\href{https://doi.org/10.1017/S0960129520000043}{https://doi.org/10.1017/S0960129520000043}.

\bibitem{BP} J.\ C.\ Baez and B.\ S.\ Pollard, A compositional framework for reaction networks, \textsl{Rev.\ Math.\ Phys.\ }\textbf{29} 
(2017), 1750028. \href{https://doi.org/10.1142/S0129055X17500283}{https://doi.org/10.1142/S0129055X17500283}.   Also available at 
\href{https://doi.org/10.48550/arXiv.1508.06448}{https://doi.org/10.48550/arXiv.1508.06448}.

@@

\bibitem{BSZ} F.\ Bonchi, P.\ Soboci\'nski and F.\ Zanasi, A categorical semantics of signal flow graphs, in \textsl{CONCUR 2014--Concurrency Theory}, 
eds.\ P.\ Baldan and D.\ Gorla, Lecture Notes in Computer Science \textbf{8704}, Springer, Berlin, 2014, pp.\ 435--450. 
\href{https://doi.org/10.1007/978-3-662-44584-6\_30}{https://doi.org/10.1007/978-3-662-44584-6\_30}.  Also available at 
\href{http://users.ecs.soton.ac.uk/ps/papers/sfg.pdf}{http://users.ecs.soton.ac.uk/ps/papers/sfg.pdf}.

@@

\bibitem{HS}  L.\ W.\ Hansen and M.\ Shulman, Constructing symmetric monoidal bicategories functorially.  Available as \href{https://doi.org/10.48550/arXiv.1910.09240}{https://doi.org/10.48550/arXiv.1910.09240}.

@@

\bibitem{KSW} P.\ Katis, N.\ Sabadini and R.\ F.\ C.\ Walters, On the algebra of systems with feedback and boundary, \textsl{Rendiconti del Circolo Matematico di Palermo Serie II} \textbf{63} (2000), 123--156.   \href{https://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.51.5758&rep=rep1&type=pdf}{https://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.51.5758\&rep=rep1\&type=pdf}.

@@

\bibitem{Lawvere} F.\ W.\ Lawvere, State categories and response functors, unpublished manuscript, 1986.  \href{https://github.com/mattearnshaw/lawvere/blob/master/pdfs/1986-state-categories-and-response-functors.pdf}{https://github.com/mattearnshaw/lawvere/blob/master/pdfs/1986-state-categories-and-response-functors.pdf}

@@

%\bibitem{RSW} R.\ Rosebrugh, N.\ Sabadini and R.\ F.\ C.\ Walters, Generic commutative separable algebras and cospans of graphs, \textsl{Theory Appl.\ Categ.\ }\textbf{15} (2005), 164--177.

%\bibitem{Reb} F.\ Rebro, Constructing the bicategory Span$_{2}(\mathrm{A})$. Available as \href{https://arxiv.org/abs/1501.00792}{arXiv:1501.00792}.

@@

\bibitem{Shulman2010} M.\ Shulman, Constructing symmetric monoidal bicategories. Available as \href{http://arxiv.org/abs/1004.0993}{arXiv:1004.0993}.

>>>>

\bibitem{BFP} J.\ C.\ Baez, B.\ Fong and B.\ S.\ Pollard, A compositional framework for Markov processes, \textsl{Jour. Math. Phys.} \textbf{57} (2016), 033301. 
\href{https://doi.org/10.1063/1.4941578}{https://doi.org/10.1063/1.4941578}. Also available at 
\href{https://doi.org/10.48550/arXiv.1508.06448}{https://doi.org/10.48550/arXiv.1508.06448}.

\bibitem{BM}  J.\ C.\ Baez and J.\ Master, Open Petri nets, \textsl{Math.\ Struct.\ Comput.\ Sci.\ }\textbf{30} (2020), 314--341.  \href{https://doi.org/10.1017/s0960129520000043}{https://doi.org/10.1017/s0960129520000043}.
Also available at
\href{https://doi.org/10.48550/arXiv.1808.05415}{https://doi.org/10.48550/arXiv.1808.05415}.

\bibitem{BP} J.\ C.\ Baez and B.\ S.\ Pollard, A compositional framework for reaction networks, \textsl{Rev.\ Math.\ Phys.\ }\textbf{29} 
(2017), 1750028. \href{https://doi.org/10.1142/S0129055X17500283}{https://doi.org/10.1142/S0129055X17500283}.   Also available at 
\href{https://doi.org/10.48550/arXiv.1704.02051}{https://doi.org/10.48550/arXiv.1704.02051}.

@@

\bibitem{BSZ} F.\ Bonchi, P.\ Soboci\'nski and F.\ Zanasi, A categorical semantics of signal flow graphs, in \textsl{CONCUR 2014--Concurrency Theory}, 
eds.\ P.\ Baldan and D.\ Gorla, Lecture Notes in Computer Science \textbf{8704}, Springer, Berlin, 2014, pp.\ 435--450. 
\href{https://doi.org/10.1007/978-3-662-44584-6\_30}{https://doi.org/10.1007/978-3-662-44584-6\_30}.  
%Also available at 
%\href{http://users.ecs.soton.ac.uk/ps/papers/sfg.pdf}{http://users.ecs.soton.ac.uk/ps/papers/sfg.pdf}.

@@

\bibitem{HS}  L.\ W.\ Hansen and M.\ Shulman, Constructing symmetric monoidal bicategories 
functorially. \href{https://doi.org/10.48550/arXiv.1910.09240}{https://doi.org/10.48550/arXiv.1910.09240}.

@@

\bibitem{KSW} P.\ Katis, N.\ Sabadini and R.\ F.\ C.\ Walters, On the algebra of systems with feedback and boundary, \textsl{Rendiconti del Circolo 
Matematico di Palermo Serie II} \textbf{63} (2000), 123--156. 
\href{https://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.51.5758&rep=rep1&type=pdf}{ 
https://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.51.5758\&rep=rep1\&type=pdf}.

@@

\bibitem{Lawvere} F.\ W.\ Lawvere, State categories and response functors, unpublished manuscript, 1986. 
\href{https://github.com/mattearnshaw/lawvere/blob/master/pdfs/1986-state-categories-and-response-functors.pdf}{
https://github.com/mattearnshaw/lawvere/blob/master/pdfs/1986-state-categories-and-response-functors.pdf}

@@

@@

\bibitem{Shulman2010} M.\ Shulman, Constructing symmetric monoidal bicategories. 
\href{https://doi.org/10.48550/arXiv.1004.0993}{https://doi.org/10.48550/arXiv.1004.0993}.
